---
title: "Loose Joined Data Drilldown"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: true
editor_options:
  chunk_output_type: console
---
<!-- author: "Julian McClellan" -->
<!-- date: "2/something/2020" -->
<!-- output:  -->
<!-- html_document: -->
<!-- toc: true -->

```{r setup, include=FALSE}
source("R/functions.R")
source("R/packages.R")
knitr::opts_chunk$set(echo = F, message = F, warning=F)
options(scipen=999) # No scientific notation

dataPBRaw <- fread("data/pricebeliefs.csv")
dataCSRaw <- fread("data/cleansample.csv") 
dataCS  <- getDataCS()
dataPB  <- getDataPB()
dataJoinedLoose  <- getDataJoined(join = "loose")
dataJoinedLooser  <- getDataJoined(join = "looser")
```

# Multiple classes per semester in the Clean Sample Data 

As was discussed in person, it may be possible for the same combination of
`email` and `period` (semester) to be represented more than once in the Clean
Sample data. I.e. someone takes two or more classes that semester that are
considered in the Clean Sample data. This could be problematic if one of the
classes was in the treatment group and the other was in the control. Both of
these clean sample rows will be joined to same row of price beliefs data but in
one joined row it will seem the student was in treatment and in the other row
it will seem like the student was in the control group, but since they had
another class that was in the treatment that same semester, that student, for
the semester, should be considered in the treatment group.

## Handling this

Before the loosely joined data is created (joining CS to PB on `email` and
`period`), we create the columns `emailPeriodCount` and `fieldCourseSum` in the
clean sample data. Thus, after the join, for each row of the loose joined data
we can determine if the student `email` for the given `period` was actually part
of the treatment group, even if that given row might have `fieldcourse = 0`. We
simply check rows for which `fieldcourse = 0` but have `fieldCourseSum >= 1`.

## Final Effect

Thankfully, there are only `r nrow(dataJoinedLoose[fieldcourse == 0 & fieldCourseSum >= 1])` rows
that have incorrectly specified treatment assignment in the loose joined data
out of `r nrow(dataJoinedLoose)` total rows. 

These rows can now be properly specified with `fieldCourseSum`.


# Drilldown of the Loose Join Data

Of the `r nrow(dataJoinedLoose)` observations we have in the final loose joined
dataset, let's investigate how these numbers breakdown in terms of `period`
(`fall12` or `spring13`), `freshdum.cs` (freshman or not), and `fieldcourse`
(`1` treatment, `0` control/non-compliant treatment).


```{r plotdrilldown}
createLooseJoinDrilldownPlot()
```

# Tracking Price Belief Updates  

3/6/2020 we discussed the possibility of tracking "updates" to students' price
beliefs. We posited that from Fall 2012 to Spring 2013, there would be a number
of students who start under the control group in Fall 2012, and from there that
`initial` group would split into an `afterTreatment` and `afterControl` group
come Spring 2013, or disappear entirely.

```{r getbeliefgroup}
updateList <- createBeliefUpdateGroups()
```

## Numbers don't work out for it

Unfortunately of the `r nrow(updateList$initial)` observations in the loose
joined data that were in the control group for Fall 2012 (`period == "fall12"`
and `fieldCourseSum == 0`), `r nrow(updateList$afterTreatment)` of them become
part of the treatment come Spring 2013 (same `email` for control in Fall 2012,
`period == "spring13"`, and `fieldCourseSum >= 1`), and `r nrow(updateList$afterControl)`
remain as part of the control group in Spring 2013 (same `email`, `period ==
"spring13"`, and `fieldCourseSum == 0`).
