---
title: "Summary Statistics"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: true
editor_options:
  chunk_output_type: console
---
<!-- author: "Julian McClellan" -->
<!-- date: "2/something/2020" -->
<!-- output:  -->
<!-- html_document: -->
<!-- toc: true -->

```{r setup, include=FALSE}
source("R/functions.R")
source("R/packages.R")
knitr::opts_chunk$set(echo = F, message = F, warning=F)
options(scipen=999) # No scientific notation

dataPBRaw <- fread("data/pricebeliefs.csv")
dataCSRaw <- fread("data/cleansample.csv") 
dataCS  <- getDataCS()
dataPB  <- getDataPB()
dataJoinedLoose  <- getDataJoined(join = "loose")
dataJoinedLooser  <- getDataJoined(join = "looser")
```

# Data Cleaning procedures

## Clean Sample 

* Initial Size: `r nrow(dataCSRaw)`
* Remove blank email addresses (`r nrow(dataCSRaw[email == ""])` in raw data).
* `period` column created with values `fall12` and `spring13` corresponding to
  `TRUE` values of `fall12dum` and `spring13dum` respectively.
* Removed responses from those with more than 10 semesters of college. (`r nrow(dataCSRaw[semesters > 10])` in raw data)
  * Note that the clean sample data and price beliefs data appear to have
    different values of `semester` and `freshdum` for the same instances of
    `email` and `period` (loose join conditions). No explanation as of yet.
* Final size: `r nrow(dataCS)`

## Price Beliefs

* Initial Size: `r nrow(dataPBRaw)`
* __Did not__ remove unfinished(?) (`finished == 0`) surveys (`r nrow(dataPBRaw[finished == 0])` did not finish?)
* `period` column created with values `fall12` and `spring13`.
  - `startyear` and `startmonth` created from original column `startdate`
  - `period=fall12` set if `startyear == 2012` and (`startmonth == 11` or `startmonth == 12`)
  - `period=spring13` set if `startyear == 2013` and `startmonth == 4`
* `mu` and `sigma` columns created to enable log-normal price distribution
  comparisons of respondent's price distribution for new books. (Uses `newexp`)
  - `mu`: `r nrow(dataPB[is.na(mu) | is.nan(mu) | is.infinite(mu)])`
    observations with `NA`, `NaN`, or `Inf` responses in the final data.
  - `sigma`: `r nrow(dataPB[is.na(sigma) | is.nan(sigma) | is.infinite(sigma)])`
    observations with `NA`, `NaN`, or `Inf` responses in the final data.
  - `mu` and `sigma`: `r nrow(dataPB[newlb + newub >= 100])` observations have
    non-sensical probability responses. (E.g. `newlb + newub >= 100` )
  - Normalized `normmu` also available. (Utilizes `newexpratio` instead of `newexp`.)
* Removed responses from those with more than 10 semesters of college (`r nrow(dataPBRaw[semesters > 10])` in raw data.)
  * Note that the clean sample data and price beliefs data appear to have
    different values of `semester` and `freshdum` for the same instances of
    `email` and `period` (loose join conditions). No explanation as of yet.
* Removed expectations of online new price that are < 10% or > 150% of the
  new bookstore price (`r nrow(dataPBRaw[newexpratio < .1 | newexpratio > 1.5])` in raw data.)
* Final size: `r nrow(dataPB)`

### Mu and Sigma Distributions for Treatment and Control Groups

```{r mu_sigma_distributions, eval = F}
### Not used, mu_sigma_dists_better used instead
indexKey <- data.table(index = 1:6,
                           indexName = c(
                                       # Fall12
                                       "nonfreshControlFall",
                                       "freshControlFall",
                                       "nonfreshTreatFall",
                                       "freshTreatFall",
                                       "nonfreshFall",
                                       "freshFall"
                                       )
)

# Data frame with combinations of freshman, treatment group, and seasons included
groupVarsDf <- list(freshVal = c(0, 1), 
                  treatVal = c(0, 1),
                  season = c("fall"),
                  dataType = c("joined", "PB")
                  ) %>%
  do.call(expand.grid, .) %>%
  mutate_at(vars(season, dataType), as.character)
groupVarsDf <- groupVarsDf[1:6,] # No treatment values in PB data

# Group that discards non-compliant treatment from control
groupList <- groupVarsDf %>%
  pmap(.f = getNormMuGroup, nonComply = F)


library(ggplot2)
(ggplot(groupList[[1]]) +
  geom_histogram(aes(normmu)) +
  labs(title = "Distribution of normmu", subtitle = paste0("Joined Data | ", indexKey[1, indexName])) +
  theme_minimal()
)

(ggplot(groupList[[1]]) +
  geom_histogram(aes(normsigma)) +
  labs(title = "Distribution of normsigma", subtitle = paste0("Joined Data | ", indexKey[1, indexName])) +
  theme_minimal()
)

(ggplot(groupList[[2]]) +
  geom_histogram(aes(normmu)) +
  labs(title = "Distribution of normmu", subtitle = paste0("Joined Data | ", indexKey[2, indexName])) +
  theme_minimal()
)

(ggplot(groupList[[2]]) +
  geom_histogram(aes(normsigma)) +
  labs(title = "Distribution of normsigma", subtitle = paste0("Joined Data | ", indexKey[2, indexName])) +
  theme_minimal()
)

(ggplot(groupList[[3]]) +
  geom_histogram(aes(normmu)) +
  labs(title = "Distribution of normmu", subtitle = paste0("Joined Data | ", indexKey[3, indexName])) +
  theme_minimal()
)

(ggplot(groupList[[3]]) +
  geom_histogram(aes(normsigma)) +
  labs(title = "Distribution of normsigma", subtitle = paste0("Joined Data | ", indexKey[3, indexName])) +
  theme_minimal()
)

(ggplot(groupList[[4]]) +
  geom_histogram(aes(normmu)) +
  labs(title = "Distribution of normmu", subtitle = paste0("Joined Data | ", indexKey[4, indexName])) +
  theme_minimal()
)

(ggplot(groupList[[4]]) +
  geom_histogram(aes(normsigma)) +
  labs(title = "Distribution of normsigma", subtitle = paste0("Joined Data | ", indexKey[4, indexName])) +
  theme_minimal()
)

(ggplot(groupList[[5]]) +
  geom_histogram(aes(normmu)) +
  labs(title = "Distribution of normmu", subtitle = paste0("Price Beliefs Data | ", indexKey[5, indexName])) +
  theme_minimal()
)

(ggplot(groupList[[5]]) +
  geom_histogram(aes(normsigma)) +
  labs(title = "Distribution of normsigma", subtitle = paste0("Price Beliefs Data | ", indexKey[5, indexName])) +
  theme_minimal()
)

(ggplot(groupList[[6]]) +
  geom_histogram(aes(normmu)) +
  labs(title = "Distribution of normmu", subtitle = paste0("Price Beliefs Data | ", indexKey[6, indexName])) +
  theme_minimal()
)

(ggplot(groupList[[6]]) +
  geom_histogram(aes(normsigma)) +
  labs(title = "Distribution of normsigma", subtitle = paste0("Price Beliefs Data | ", indexKey[6, indexName])) +
  theme_minimal()
)
```

```{r mu_sigma_dists_better}
muSigmaPB <- dataPB %>%
  filter(period == "fall12",
         is.finite(normmu),
         is.finite(normsigma),
         newlb + newub < 100
         ) %>%
  mutate(group = case_when(freshdum == 1 ~ "freshFall",
                           freshdum == 0 ~ "nonfreshFall",
                           TRUE ~ "ignore"),
         normsigmasqr = normsigma ^ 2
         ) %>%
  filter(group != "ignore") %>%
  group_by(group) %>%
  add_tally() %>%
  mutate(n = factor(n, levels = sort(unique(.$n))),
         normmuMean = mean(normmu),
         normsigmaMean = mean(normsigma),
         normsigmasqrMean = mean(normsigmasqr)
         )

muSigmaJoined <- dataJoinedLoose %>%
  filter(period == "fall12",
         is.finite(normmu),
         is.finite(normsigma),
         newlb + newub < 100
         ) %>%
  mutate(group = case_when(freshdum.pb == 1 & treatme == 1 & offered == 1 ~ "freshTreatFall",
                           freshdum.pb == 1 & treatme == 0 & offered == 0 ~ "freshControlFall",
                           freshdum.pb == 0 & treatme == 1 & offered == 1 ~ "nonfreshTreatFall",
                           freshdum.pb == 0 & treatme == 0 & offered == 0 ~ "nonfreshControlFall",
                           TRUE ~ "ignore"),
         freshPB = case_when(freshdum.pb == 1 ~ "Fresh",
                             freshdum.pb == 0 ~ "nonFresh"
                             ),
         treatControl = case_when(treatme == 1 & offered == 1 ~ "Treat",
                                  treatme == 0 & offered == 0 ~ "Control"),
         normsigmasqr = normsigma ^ 2
         ) %>%
  filter(group != "ignore") %>%
  group_by(group) %>%
  add_tally() %>%
  mutate(n = factor(n, levels = sort(unique(.$n))),
         normmuMean = mean(normmu),
         normsigmaMean = mean(normsigma),
         normsigmasqrMean = mean(normsigmasqr)
         )

library(ggplot2)
# Density
(ggplot(muSigmaPB) +
  geom_density(aes(normmu, fill = n)) +
  labs(title = "Distribution of normmu (Fall12 Only, Mean Plotted)", subtitle = "Price Beliefs Data") +
  theme_minimal() +
  facet_grid(group ~ .) +
  geom_vline(aes(xintercept = normmuMean), linetype = "dotted") +
  theme(strip.text.y = element_text(angle = 0, hjust = 1))
)

(ggplot(muSigmaPB) +
  geom_density(aes(normsigma, fill = n)) +
  labs(title = "Distribution of normsigma (Fall12 Only, Mean Plotted)", subtitle = "Price Beliefs Data") +
  theme_minimal() +
  facet_grid(group ~ .) +
  geom_vline(aes(xintercept = normsigmaMean), linetype = "dotted") +
  theme(strip.text.y = element_text(angle = 0, hjust = 1))
)

# (ggplot(muSigmaPB) +
#   geom_density(aes(normsigmasqr, fill = n)) +
#   labs(title = "Distribution of normsigmasqr (Fall12 Only, Mean Plotted)", subtitle = "Price Beliefs Data") +
#   theme_minimal() +
#   facet_grid(group ~ .) +
#   geom_vline(aes(xintercept = normsigmasqrMean), linetype = "dotted") +
#   theme(strip.text.y = element_text(angle = 0, hjust = 1)) +
#   scale_x_continuous(limits = c(0, 1)) + 
#   scale_y_continuous(limits = c(0, 50))
# )

(ggplot(muSigmaJoined) +
  geom_density(aes(normmu, fill = n)) +
  labs(title = "Distribution of normmu (Fall12 Only, Mean Plotted)", subtitle = "Loose Joined Data") +
  theme_minimal() +
  facet_grid(group ~ .) +
  geom_vline(aes(xintercept = normmuMean), linetype = "dotted") +
  theme(strip.text.y = element_text(angle = 0, hjust = 1))
)

(ggplot(arrange(muSigmaJoined, n)) +
  geom_density(aes(normsigma, fill = n)) +
  labs(title = "Distribution of normsigma (Fall12 Only, Mean Plotted)", subtitle = "Loose Joined Data") +
  theme_minimal() +
  geom_vline(aes(xintercept = normsigmaMean), linetype = "dotted") +
  facet_grid(group ~ .) +
  theme(strip.text.y = element_text(angle = 0, hjust = 1))
)

# (ggplot(arrange(muSigmaJoined, n)) +
#   geom_density(aes(normsigmasqr, fill = n)) +
#   labs(title = "Distribution of normsigmasqr (Fall12 Only, Mean Plotted)", subtitle = "Loose Joined Data") +
#   theme_minimal() +
#   geom_vline(aes(xintercept = normsigmasqrMean), linetype = "dotted") +
#   facet_grid(group ~ .) +
#   theme(strip.text.y = element_text(angle = 0, hjust = 1))
# )

# Histograms
(ggplot(muSigmaPB) +
  geom_histogram(aes(normmu, fill = n), binwidth = .1) +
  labs(title = "Histogram of normmu (Fall12 Only, Mean Plotted)", subtitle = "Price Beliefs Data | Binwidth = .1") +
  theme_minimal() +
  geom_vline(aes(xintercept = normmuMean), linetype = "dotted") +
  facet_grid(group ~ .) +
  theme(strip.text.y = element_text(angle = 0, hjust = 1))
)

(ggplot(muSigmaPB) +
  geom_histogram(aes(normsigma, fill = n), binwidth = .1) +
  labs(title = "Histogram of normsigma (Fall12 Only, Mean Plotted)", subtitle = "Price Beliefs Data | Binwidth = .1") +
  geom_vline(aes(xintercept = normsigmaMean), linetype = "dotted") +
  theme_minimal() +
  facet_grid(group ~ .) +
  theme(strip.text.y = element_text(angle = 0, hjust = 1))
)

# (ggplot(muSigmaPB) +
#   geom_histogram(aes(normsigmasqr, fill = n), binwidth = .1) +
#   labs(title = "Histogram of normsigmasqr (Fall12 Only, Mean Plotted)", subtitle = "Price Beliefs Data | Binwidth = .25") +
#   geom_vline(aes(xintercept = normsigmasqrMean), linetype = "dotted") +
#   theme_minimal() +
#   facet_grid(group ~ .) +
#   theme(strip.text.y = element_text(angle = 0, hjust = 1)) +
#   scale_x_continuous(limits = c(0, 9)) + 
#   scale_y_continuous(limits = c(0, 50))
# )

(ggplot(muSigmaJoined) +
  geom_histogram(aes(normmu, fill = n), binwidth = .1) +
  labs(title = "Histogram of normmu (Fall12 Only, Mean Plotted)", subtitle = "Loose Joined Data | Binwidth = .1") +
  geom_vline(aes(xintercept = normmuMean), linetype = "dotted") +
  theme_minimal() +
  facet_grid(group ~ .) +
  theme(strip.text.y = element_text(angle = 0, hjust = 1))
)

(ggplot(arrange(muSigmaJoined, n)) +
  geom_histogram(aes(normsigma, fill = n), binwidth = .1) +
  labs(title = "Histogram of normsigma (Fall12 Only, Mean Plotted)", subtitle = "Loose Joined Data | Binwidth = .1") +
  geom_vline(aes(xintercept = normsigmaMean), linetype = "dotted") +
  theme_minimal() +
  facet_grid(group ~ .) +
  theme(strip.text.y = element_text(angle = 0, hjust = 1))
)
 
# (ggplot(arrange(muSigmaJoined, n)) +
#   geom_histogram(aes(normsigmasqr, fill = n), binwidth = .25) +
#   labs(title = "Histogram of normsigmasqr (Fall12 Only, Mean Plotted)", subtitle = "Loose Joined Data | Binwidth = .25") +
#   geom_vline(aes(xintercept = normsigmasqrMean), linetype = "dotted") +
#   theme_minimal() +
#   facet_grid(group ~ .) +
#   theme(strip.text.y = element_text(angle = 0, hjust = 1)) + 
#   scale_x_continuous(limits = c(0, 9)) + 
#   scale_y_continuous(limits = c(0, 50))
# )
```

### Ongoing Price Belief Work


#### Non-sensical expectation filtering

In [this paper](https://www.sciencedirect.com/science/article/pii/S016726811630021X?via%3Dihub#fn0060)
they drop nonsensical answers; expectations less than 10% or greater than 150%
of the bookstore price. However, the price beliefs data has expectation ratio
columns for new, used, and rent prices. I'm assuming they only use the new expectation ratios?

```{r pbexpratioclean, echo=T}
(
 pbRatios <- names(dataJoinedLoose)[grepl("ratio", names(dataJoinedLoose))]
)
```

#### Price-belief with no treatment/control information (can't join to Clean Sample data)

```{r pbonly}
createPBOnlyBreakdownPlot()
```

# Plots for Clean Sample Data 

## Treatment Breakdown: Obs Level
```{r cs_gtreat, include=TRUE}
createTreatmentPlot("cs", dataCS)
```

### Freshman Status
```{r, include=TRUE}
createTreatmentPlotFreshman("cs", dataCS)
```

### Class in Student Major?
```{r, include=TRUE}
createTreatmentPlotMajorClass("cs", dataCS)
```

## Treatment Breakdown: Classes Level
```{r cs_gtreatclass, include=TRUE}
createTreatmentPlotClasses("cs", dataCS)
```

### Classes: Book Price Comparison
```{r cs_gtreatbprice, include=TRUE}
createTreatmentPlotClassesPriceDiff("cs", dataCS)
```



# Plots for Loose Joined Data

## Overview of Join

The "loose" joined data joins the clean sample and price beliefs tables on
`email` and `period`. Period joins are allowed only if the `period` of the
clean sample is the same as the price beliefs `period`.

## Treatment Breakdown: Obs Level
```{r, include=TRUE}
createTreatmentPlot("loose", dataJoinedLoose)
```

### Freshman Status
```{r, include=TRUE}
createTreatmentPlotFreshman("loose", dataJoinedLoose)
```

### Class in Student Major?
```{r, include=TRUE}
createTreatmentPlotMajorClass("loose", dataJoinedLoose)
```

## Treatment Breakdown: Classes Level
```{r, include=TRUE}
createTreatmentPlotClasses("loose", dataJoinedLoose)
```

### Classes: Book Price Comparison
```{r, include=TRUE}
createTreatmentPlotClassesPriceDiff("loose", dataJoinedLoose)
```

# Plots for Looser Joined Data

## Overview of Join

The "looser" joined data joins the clean sample and price beliefs tables on
`email` and `period`. Period joins are allowed as long as the `period` of the
clean sample occurs during the same `period` or earlier than the price beliefs.
`period.cs <= period.pb`

## Treatment Breakdown: Obs Level
```{r, include=TRUE}
createTreatmentPlot("looser", dataJoinedLooser)
```

### Freshman Status
```{r, include=TRUE}
createTreatmentPlotFreshman("looser", dataJoinedLooser)
```

### Class in Student Major?
```{r, include=TRUE}
createTreatmentPlotMajorClass("looser", dataJoinedLooser)
```

## Treatment Breakdown: Classes Level
```{r, include=TRUE}
createTreatmentPlotClasses("looser", dataJoinedLooser)
```

### Classes: Book Price Comparison
```{r, include=TRUE}
createTreatmentPlotClassesPriceDiff("looser", dataJoinedLooser)
```
